Neural Style Transfer on Text\\Project Report One

### 2017-11-12 dl-style-transfer/reports/src/project_report_another_one.tex
Wrote project report

The current state of the project is rather fluid. Having studied current advances
in Style Trasfer and recreated Gatys' original model, we are currently studying
the feasibility of style transfer on text using a similar method. There are a number
of obstacles in this regard, including finding a feasible model for text reconstruction,
studying the properties of style in text, and the possibility of connecting these
two concepts in an extension of existing style transfer work. This group is currently
working on the development of

@@

The current objective of our work has been to research the viability of a variety of text representation models, and the viability of text reconstruction using these methods. Work has been done in using CNNs and autoencoders for text representation. Currently,
the models are still in the process of being implemented, an analysis of their viability for text representation is pending.

@@

At this point in the process, the team is still constructing a number of different models
for text representation. Viable candidates include, CNNs, Varaitional Autoencoders, and KATE. Using these, we will study the possiblity of text representation over the next week.

@@

	\item [Yuji Akimoto]
		Implemented image style transfer with VGG-16 trained on CIFAR-10 data instead of ImageNet data, to see if ``content'' representations of images would still be general enough. Also implemented (untrained) ``Shallow-CNN'', a popular convolutional architecture for text classification as described by [Yoon Kim](https://arxiv.org/abs/1408.5882).

	\item [Ryan Butler]

	\item [Cameron Ibrahim]
		Attempting to implement the KATE autoencoder.
		Generated vector representations of the Yelp review vocabulary.

	\item [Luca Leeser]
		Implemented a variational autoencoder.

@@

We intend to study the layer by layer representation of text in our models and intend to implement text reconstruction. From there, we will begin to study style representation of text.

\section{References}

>>>>

The exploratory period of this project is quickly coming to a close, and we're ramping up our 
effort to get definite results. At this time, we are likely going to be using a CNN based
architecture, in collaboration with competitive layers - either integrated into the layers of the CNN themselves,
or added to the end of the network, as in the style of the Fully Connected Nets commonly added to the end of CNN
architectures. Additionally, we are currently putting together a dataset of alternative text sources, to address
our need for more distinct styles for experiment purposes. We will be training an initial CNN architecture later
today.

@@

Our current research has moved into a more experimental stage, as we begin to train the inital models we have created. These experiments will be
use a 10 book dataset of distinct styles. The hope is that this will allow us to more easily determine success and failure. Failure here would 
render our model unviable for use with Yelp

@@

We are currentlly in the process of training our initial models to begin experiments. Loss function has shown improvement. Created a 10 book dataset of sentences
for training uses.

@@

	\item [Yuji Akimoto]
		Improved an initial CNN based architecture for text representation. Has yet to be trained.

	\item [Ryan Butler]
		Further research into KATE, Discrete Autoencoders, and other methods we may be interested in incorporating into our model.

	\item [Cameron Ibrahim]
		Assembling the dataset of a number of books pulled from Project Gutenberg. Training Yuji's model. Generated word embeddings for dataset.

	\item [Luca Leeser]
		Further refined the facenet L2 based loss function for use with text.

@@

In the event of total failure of our models, we will pivot to trying to explain exactly \emph{why} our methods have not worked. This in itself would make up an interesting research topic, and would easily fill the paper.
\section{References}
